\sysfull

### 2018-04-15 paper/evaluation.tex

@@

We first need to assess the performance of all coalescing strategies intriduced by us in Section~\ref{}.

>>>>

\textcolor{red}{ highlight the difference between Alpaca GCC and Alpaca Clang. Alpaca GCC is about 30\%-40\% faster than Alpaca Clang. Writing Alpaca program by hand is a very trick thing and it is very error prone. Reason: a programmer needs to identify the write-after-read dependencies, change variables' names, and modify instructions accordingly, in general writing Alpaca code by hand is not a recommended, for that a compiler is needed}

@@

We first need to assess the performance of all coalescing strategies introduced by us in Section~\ref{}.
